---
title: "DSlecture8"
author: "Hening cui"
date: "2021/10/5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggridges)
```



```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```
## scatter plot

first scatter plot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + geom_point()
```


New approach
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point()
```

Save and edit a plot object
```{r}
weather_plot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```


## advance scatter plot

start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + geom_point() + geom_smooth(se = FALSE)
```

what is about the aes placement
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point(aes(color = name)) + geom_smooth(se = FALSE)
```

let facet sth

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid( name ~.)
```

define transparency
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .2, size = .3) + 
  geom_smooth(se = FALSE, size = 2) +
  facet_grid( . ~ name)
```

the alpha could be variable
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) + 
  geom_point( size = .3) + 
  geom_smooth(se = FALSE, size = 2) +
  facet_grid( . ~ name)
```

combine some elements

```{r}
weather_df  %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp, alpha = 0.5)) +
  geom_smooth(se = FALSE)  + 
  facet_grid(.~ name)
```

## Some small notes

how many geoms have to exist

```{r}
weather_df %>% 
  ggplot( aes (x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

you can use a neat geom
for population is big, scatter point is hard to see
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_bin2d()
```
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density_2d() + geom_point( alpha = 0.3)
```


## univariate plot
one variable a time

histograms are really great

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

can we add color

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge")
```
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(.~name)
```


let try a new geometry
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density( alpha = 0.3)

```

what about boxplot
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```


Trendy plot
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = 0.3) + 
  stat_summary()
```
ridge plots

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name))+
  geom_density_ridges()
```




